% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
%For any Clarification please contact 
% Mr. Narayanan P.P., AP ECE of Royal College of Engineering and technology, Akikkavu %%
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %


\documentclass[12pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\linespread{1.5}
\usepackage{times}
\usepackage{tikz}
\usepackage{graphicx,ragged2e,setspace,fancyhdr,enumerate,makeidx,setspace,nomencl,eso-pic,xcolor,lipsum,calc,pst-node,tikz,fancybox,caption,subcaption,amsfonts}
\usetikzlibrary{calc}
\usepackage[final]{pdfpages}
\usepackage[left=3.2cm,right=2.5cm,top=2.5cm,bottom=2.5cm]{geometry} 
\usepackage{fancyhdr}
\pagestyle{fancy}



\usepackage{titlesec}
\titleformat{\chapter}[display]
{\normalfont\huge\bfseries\centering}{\chaptertitlename\ \thechapter}{20pt}{\Huge}


\begin{document}


%%%%%%%%%% 
%for editing Coverpage/certificate page/ acknowledgement/ Abstratct please select the appropriatete section in the left panel (Structure) edit the required field, Save it and then run this report .tex file
%%%%%%%%%%


\input{Coverpage}
\newpage
\pagenumbering{roman}
\input{certificate}
\addcontentsline{toc}{chapter}{\quad CERTIFICATE}
\newpage


\input{headerfooter}

\input{Dedicationpage}
%\newpage
\input{Acknoledgement}
\addcontentsline{toc}{chapter}{\quad ACKNOWLEDGEMENT}
%\newpage
\input{Abstract}
\addcontentsline{toc}{chapter}{\quad ABSTRACT}
%\newpage
\tableofcontents
\newpage
\listoffigures
\addcontentsline{toc}{chapter}{\quad LIST OF FIGURES}
\newpage
\listoftables
\addcontentsline{toc}{chapter}{\quad LIST OF TABLES}
\input{nomenclature}
\addcontentsline{toc}{chapter}{\quad LIST OF SYMBOLS AND ABBREVIATIONS}


\newpage
\pagenumbering{arabic}
\chapter {INTRODUCTION}


{ Give some introduction about the project . . .}


\section{Background}
Background..


\section{Motivation}
Motivation..

\section{Objectives}

Objectives..


\section{Scope of the Project}
What is the scope of the project in present scenario.

\section{Report Organization}

The thesis contains 6 chapters. Chapter 1 gives the introduction to the project work and describes the objectives of the work. Literature survey is describes in Chapter 2. An introduction to the pro............


\chapter{LITERATURE REVIEW}

{Write detailed literature survey done for the project.}





\chapter{Proposed System Model}


{Write the entire concept that you proposed. the chapter may include: Block diagram, Circuit Diagram, Descriptions, Designs.. etc.}
\section{Block diagram}
Block diagram and its description

\section{Circuit Diagram}
circuit diagram and its working.

\section{Design}
Design for the circuit

\chapter{HARDWARE IMPLEMENTATION}

The Hardware . . .


\chapter{Software Tools Used and Programming}

{ Write about the Software tools used for the project. also include the Algorithm and flow charts required for the program}

\section{Software Tools used}
Software tools description.

\section{Algorithm}
Algorithm

\section{Flow-chart}
Flowchart

\chapter{SIMULATION \& RESULTS}

Simulation results... Output of the system, discussions. inference etc..


\chapter{CONCLUSION}

Summarize and conclude your project



\chapter*{\centering{APPENDIX}}
\addcontentsline{toc}{chapter}{\quad APPENDIX}

You may include Program code, data sheets, or any other technical contents required for the project in appendix. set separate sections for each.
\section*{APPENDIX-1-Program code for ABC}


{Write the code here: required for the purpose ABC}


\newpage
\section*{APPENDIX-2-Data sheet of XYZ}

{input only the required sheets of data sheet of XYZ if required. Don't insert those sheets which are not mandatory.}


\newpage
\section*{APPENDIX-3- Other technical contents }

{write any other required technical contents.}


\chapter*{REFERENCES}

\begin{enumerate}[{[1]}]
\item R. Mesleh, H. Haas, S. Sinanovic, C. W. Ahn, and S. Yun, “Spatial modulation” IEEE Trans. Veh. Technol., vol. 57, no.4, pp. 2228-2241, Jul. 2008.
\item M. D. Renzo, H. Haas, and P. M. Grant, “Spatial modulation for multiple antenna wireless systems - A survey,” IEEE Commun. Mag., vol. 49, no.12, pp. 182- 191, Dec. 2011.
\item Jeganathan, Jeyadeepan, Ali Ghrayeb, and Leszek Szczecinski, "Spatial modulation: optimal detection and performance analysis," Communications Letters, vol.12, no.8, pp. 545-547, Aug. 2008.

\end{enumerate}


\addcontentsline{toc}{chapter}{\quad PUBLICATIONS RELATED TO THIS WORK}
\chapter*{\centering{Publications Related to this Work}}



\begin{enumerate}
\item{Write the details of the conferences/ journals in which your topic were published (if any)}
\item{ details of conference-2 paper etc..}

\end{enumerate}



\end{document}